---
title: "Lcrispatus_summary.RMD"
author: "Leah Boger"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Define directory path
ani_directory <- "/Users/leahboger/Desktop/Lgasseri_ANI/"

# Define filenames (Still working out how we can implement this aspect into python)
file_names <- c(""))

# Read and process ANI files
ani_data <- list()
for (file_name in file_names) {
  file_path <- paste0(ani_directory, file_name)
  ani <- readr::read_tsv(file_path, col_names = FALSE)
  ani_data[[file_name]] <- data.frame(ani[, 3])
}

# Calculate lengths of ANI vectors
ani_lengths <- sapply(ani_data, length)

# Combine ANI vectors into a single vector
y <- unlist(ani_data)

# Create strain vector
strains <- rep(c("lgasseri10", "lgasseri53", "lgasseri54", "lgasseri56"), each = 25)

l <- lm(y~strain)

anova(l)
#low p-value (< 2.2e-16), reject null hypothesis -- (null is there is not sig strain difference)

shapiro.test(l$residuals)
#low p-val(9.893e-15), reject null (null is that the residuals follow a normal distribution)

bartlett.test(l$resid, strain)
#low p-val (< 2.2e-16), assumption of homoscedasticity not met

#use nonparametric ANOVA, aka kruskal.test
kruskal.test(y~strain)
#small p-val(< 2.2e-16), so appears to be significant difference between strains

```

```{r}
TukeyHSD(aov(y~strain), conf.level=0.95)
library(agricolae)
an.m<-aov(y~strain)
l<- LSD.test(an.m,"strain",p.adj = "bonferroni")
l
```



```{r}
all<-y #compiling all the ANI values together      (why make new variable)
boot<-sample(all,size=10000,replace = TRUE) #bootstrap
d<-density(boot) #kernel density estimation
library(ggplot2)
library(dplyr)
df<-data.frame(boot)
```

```{r}
library(tidyverse)
testANI <- read.table(pipe("pbpaste"), sep="\t", header = TRUE)

testANI$strain_loc1 <- paste(testANI$X, testANI$X.1)

testANI <- testANI %>% select(#need to select specific strains
)

columns = paste(names(testANI),as.matrix(testANI[1,]))
colnames(testANI) = columns

testANI <- testANI[-1, ]
colnames(testANI)[1] ="strain_loc1"

testANI <- testANI %>% pivot_longer(-strain_loc1, names_to = "strain_loc2", values_to = "ANI")

testANI$ANI <- as.numeric(testANI$ANI)
emp<-rep(0,nrow(testANI))
for(i in 1:nrow(testANI))
  {emp[i]<-pemp(testANI$ANI[i],boot, prob.method = "emp.probs")}
t<-cbind(testANI,emp)

#from here onwards we need to plot all the results
#for plots we will need to write out p val then pull back in to generate output for ggplot
